### 2014-03-11 Studies/Chicago_2012/Report/Chicago_Fire.tex
Chicago Fire: working on tables

On November 2, 2012, a fire in a 2 1/2 story wood frame residential structure resulted in the death of a fire captain and injury to a fire fighter.  At approximately 5:16 in the afternoon, a dispatch was made for ``smoke in the area''.   Within a minute of dispatch, a Battalion Chief (BC) arrived and sized up the structure fire from the exterior and reported a working fire with heavy smoke coming from the front and rear of the structure's attic.  After speaking with the building occupants, the BC entered the structure and found light smoke on the second floor and a glow around the doorway that led from the second floor hallway to enclosed rear porch.  Engine 123 arrived on scene at approximately 17:19. The victims were part of the Engine 123 crew.  The BC met the Captain and the Fire Fighter (victims) at the front door to the structure.  Then the Captain and Fire Fighter took their hose line to the second floor of the structure.  At approximately 5:21, the Captain and Fire Fighter are on the second floor with their hoseline and had begun advancing the charged line toward the rear second floor door between the apartment and the enclosed porch.   Approximately 30 seconds later, a fire fighter from Tower Ladder 39 (TL 39) enters the enclosed porch on the rear of the structure by opening the rear exterior door to the first floor of the porch.   The fire fighter from TL 39, notices ``the fire light up'' in the stairwell of the enclosed porch, and then kicks in the first level door between the rear porch and the main structure.   Both doors remain open and the fire fighter from TL 39 exits the structure.  Given the amount of fire showing from the second floor of the rear porch and ``heavy fire'' in the stairwell of the rear porch, the BC radios the Engine 123 Captain at 17:23, to alert him to the fire conditions and to advise him that Engine 49 would be applying water to the fire on the rear of the structure from the exterior.  No response was made by the Engine 123 Captain.  It is believed that the door between the rear porch and the second floor hallway, where the Engine 123 Captain and Fire Fighter were located may have failed by this time.  Approximately a minute later Engine 49 applied water to the fire in the attic.

Squad 5 entered the front of the structure at approximately 17:25 and headed to the second floor.  They heard a commotion and found the Engine 123 Captain collapsed on the kitchen floor and entangled with the Engine 123 firefighter.  A Mayday was called on the radio by Squad 5 at approximately  17:27 and the Engine 123 Captain was removed from the front of the building at approximately 17:29 and succumbed to his injuries at the hospital at 17:38. Table~\ref{tab:fire_info} presents the timeline of the fire.

\bigskip 
\begin{minipage}{.8\linewidth}
\centering
\captionof{table}{Fire Event Timeline}\label{tab:fire_info}
\begin{tabular}{c m{0.25in}}
\toprule[1.5pt]
Incident Time & Fire Behavior / Fireground Operation  \\
\midrule
17:15    & Reported working fire with heavy smoke coming from the front and rear of the structure's attic. \\
17:16    & Dispatch for a {\bf Still Alarm} \\
17:20    & Attic self ventilation - heavy smoke out of front attic window and heavy smoke and fire out of rear. \\  
17:21:00 & Engine 123 Capt. and FF on 2$^{nd}$ floor with 1 3/4-in hose line. \\
17:21:30 & 1$^{st}$ floor exterior porch door opened. \\
17:23    & Heavy fire report in rear stairwell and enclosed porch. No response from Engine 123: Capt. or FF. \\
17:24    & Water applied to attic from the rear exterior position. \\
17:27    & IC calls a Mayday \\
17:29    & Engine 123 Capt. carried out of structure. \\
\bottomrule[1.25pt]
\end{tabular}\par
\bigskip
\end{minipage}

>>>>

On November 2, 2012, a fire in a 2 1/2 story wood frame residential structure resulted in the death of a fire captain and injury to a fire fighter. At approximately 5:16 in the afternoon, a dispatch was made for ``smoke in the area''. Within a minute of dispatch, a Battalion Chief (BC) arrived and sized up the structure fire from the exterior and reported a working fire with heavy smoke coming from the front and rear of the structure's attic. After speaking with the building occupants, the BC entered the structure and found light smoke on the second floor and a glow around the doorway that led from the second floor hallway to enclosed rear porch. Engine 123 (E123) arrived on scene at approximately 17:19. The victims were part of the E123 crew.  The BC met the Captain and the Firefighter (victims) at the front door to the structure.  Then the Captain and Firefighter took their hose line to the second floor of the structure. At approximately 5:21, the Captain and Fire Fighter are on the second floor with their hoseline and had begun advancing the charged line toward the rear second floor door between the apartment and the enclosed porch. Approximately 30 seconds later, a fire fighter from Tower Ladder 39 (TL39) enters the enclosed porch on the rear of the structure by opening the rear exterior door to the first floor of the porch. The firefighter from TL39, notices ``the fire light up'' in the stairwell of the enclosed porch, and then kicks in the first level door between the rear porch and the main structure. Both doors remain open and the firefighter from TL39 exits the structure. Given the amount of fire showing from the second floor of the rear porch and ``heavy fire'' in the stairwell of the rear porch, the BC radios the E123 Captain at 17:23, to alert him to the fire conditions and to advise him that E49 would be applying water to the fire on the rear of the structure from the exterior. No response was made by the E123 Captain. It is believed that the door between the rear porch and the second floor hallway, where the E123 Captain and firefighter were located may have failed by this time.  Approximately a minute later E49 applied water to the fire in the attic.

Squad 5 (S5) entered the front of the structure at approximately 17:25 and headed to the second floor. They heard a commotion and found the E123 Captain collapsed on the kitchen floor and entangled with the E123 firefighter. A Mayday was called on the radio by S5 at approximately  17:27 and the E123 Captain was removed from the front of the building at approximately 17:29 and succumbed to his injuries at the hospital at 17:38. Table~\ref{tab:fire_info} presents the timeline of the fire.

\begin{table}[!h]
\centering
\captionof{table}{Fire Event Timeline}\label{tab:fire_info}
\begin{tabularx}{0.8\textwidth}{c p{3cm}}
\toprule[1.5pt]
Incident Time & Fire Behavior / Fireground Operation  \\
\midrule
17:15    & Reported working fire with heavy smoke coming from the front and rear of the structure's attic. \\
17:16    & Dispatch for a {\bf Still Alarm} \\
17:20    & Attic self ventilation - heavy smoke out of front attic window and heavy smoke and fire out of rear. \\  
17:21:00 & E123 Capt. and FF on 2$^{nd}$ floor with 1 3/4-in hose line. \\
17:21:30 & 1$^{st}$ floor exterior porch door opened. \\
17:23    & Heavy fire report in rear stairwell and enclosed porch. No response from E123: Capt. or FF. \\
17:24    & Water applied to attic from the rear exterior position. \\
17:27    & IC calls a Mayday \\
17:29    & E123 Capt. carried out of structure. \\
\bottomrule[1.25pt]
\end{tabularx}
\end{table}
